### 2018-04-30 paper/message-passing-design.tex
removed comments

Bob then sends \Hrecforward and the descriptors of the \LRV nodes to Alice, by calling Alice's \Send function (also in figure~\ref{fig:route building algo}).
like Bob, Alice randomly picks nodes to constitutes $l$ layers from her \squad to \LRV.
She also builds two encrypted headers: \Hsendforward contains the route from her \squad (excluded) to \LRV (included), while \Hsendbackward contains the route from \LRV (excluded) to her \squad (included).
Alice finally sends \Hsendbackward back to Bob.

Back to Bob's \Recv

\paragraph*{Layer creation}

The

\paragraph*{Header preparation}

@@

      \State $\Hbackward \gets \Hrecbackward \concat \Hsendbackward$
      %\State $H_\rdv\gets \ExtendRoute[D\concat \top, L, \theta]$
      % \State \Return $H_\rdv$
      %   \Comment{Give to sender out-of-bound.}
    \EndFunction
  \end{algorithmic}
  %\end{minipage}}

  \vspace{0.3em}
  %\framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}[1]
    % \Require{%
    %   $m$ is the message to be sent,
    %   $H_\rdv$ is the onion-route given by the recipient.
    % }
    \Function{\Send}{\Hrecforward, \LRV}
      \State layers $\gets [\,]$
      \While{len(layers) $ < l$}
        \State layers.append(\CreateOnionLayer())
      \EndWhile
      \State $\Hsendforward \gets$ properly encrypted layers
      \State $\Hsendbackward \gets$ properly encrypted layers
      \State $\Hforward \gets \Hsendforward \concat \Hrecforward$
      \State \Return \Hsendbackward

@@

  \begin{algorithmic}[1]
    \Function{\CreateOnionLayer}{\null}
      \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
      \State $\mathcal{L}\gets \{(d, \pk_d, p_d)\}$
      \While{$\prod_{d\in \mathcal{L}} p_d > \theta$}
        \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
        \State $\mathcal{L}\gets \mathcal{L}\cup \{(d, \pk_d, p_d)\}$
      \EndWhile
      \State \Return $\mathcal{L}$
    \EndFunction
  \end{algorithmic}
  %\end{minipage}}
  \caption{\label{fig:route building algo}The route building algorithm}
\end{figure}

>>>>

Bob then sends \Hrecforward and the descriptors of the \LRV nodes to Alice, by calling Alice's \Send function (also in figure~\ref{fig:route building algo}).
like Bob, Alice randomly picks nodes to constitutes $l$ layers from her \squad to \LRV.
She also builds two encrypted headers: \Hsendforward contains the route from her \squad (excluded) to \LRV (included), while \Hsendbackward contains the route from \LRV (excluded) to her \squad (included).
Alice now ha the full forward header \Hforward, as shown on line~\ref{hforward}
Alice finally sends \Hsendbackward back to Bob.

Back to \Recv function: Bob has the full backward header $\Hbackward$, as shown on line~\ref{hbackward}.

\paragraph*{Layer creation}
The function \CreateOnionLayer() iteratively add random nodes (from the RPS's view \view) until the product $\prod_{d\in \mathcal{L}} (1 - p_d)$ falls below $\theta$.
$(1 - p_d)$ is the probability that a device $d$ will be offline; the product is the probability that all devices on layer $\mathcal{L}$ fall offline at the same time.

%\paragraph*{Header preparation}

@@

      \State $\Hbackward \gets \Hrecbackward \concat \Hsendbackward$ \label{hbackward}
      %\State $H_\rdv\gets \ExtendRoute[D\concat \top, L, \theta]$
      % \State \Return $H_\rdv$
      %   \Comment{Give to sender out-of-bound.}
    \EndFunction
  \end{algorithmic}
  %\end{minipage}}

  \vspace{0.3em}
  %\framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}[1]
    % \Require{%
    %   $m$ is the message to be sent,
    %   $H_\rdv$ is the onion-route given by the recipient.
    % }
    \Function{\Send}{\Hrecforward, \LRV}
      \State layers $\gets [\,]$
      \While{len(layers) $ < l$}
        \State layers.append(\CreateOnionLayer())
      \EndWhile
      \State $\Hsendforward \gets$ properly encrypted layers
      \State $\Hsendbackward \gets$ properly encrypted layers
      \State $\Hforward \gets \Hsendforward \concat \Hrecforward$ \label{hforward}
      \State \Return \Hsendbackward

@@

  \begin{algorithmic}[1]
    \Function{\CreateOnionLayer}{\null}
      \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
      \State $\mathcal{L}\gets \{(d, \pk_d, p_d)\}$
      \While{$\prod_{d\in \mathcal{L}} (1 - p_d) \geq \theta$}
        \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
        \State $\mathcal{L}\gets \mathcal{L}\cup \{(d, \pk_d, p_d)\}$
      \EndWhile
      \State \Return $\mathcal{L}$
    \EndFunction
  \end{algorithmic}
  %\end{minipage}}
  \caption{\label{fig:route building algo}The route building algorithm}
\end{figure}
